---
title: "Tunning Support Vector Machine Model"
author: "Joseph Oladokun"
date: "October 23, 2018"
output: html_document
---
library(ISLR)
library(e1071)

```{r}
print(head(iris))
```

## SVM Model

Build your Support Vector Machine Model Using the IRIS dataset

```{r model}
model <- svm(Species ~ ., data = iris)
```

## Summary

Get the Model Summary

```{r summary}
summary(model)
```

Let's tune the cost and the gamma to get the best possible error rate
```{r}
tune.results <- tune(svm,train.x = iris[1:4],train.y = iris[,5],kernel = 'radial', 
                     ranges = list(cost=c(0.1,1,10), gamma = c(0.5,1,2)))
summary(tune.results)
```
The table above shows 1.0 and 0.5 will give us the best error rate. Lets tune between these values
```{r}
tune.results <- tune(svm,train.x = iris[1:4],train.y = iris[,5],kernel = 'radial', 
                     ranges = list(cost=c(0.5,1,1.5), gamma = c(0.1,0.5,0.7)))
summary(tune.results)
```
Now when the values of cost = 1.5 and gamma = 0.1 we have the best error rate.
You can keep tunning around those figures to get the best possible error rates.
```{r}
tuned.svm <- svm(Species ~ ., data = iris, kernel = "radial", cost = 1.5, gamma = 0.1)
summary(tuned.svm)
```
